Dark matter halo concentrations with a bayesian approach

### 2014-05-26 paper/article.tex
minor updates
new paragaph

The method we use to generate the halos is based on the integrated
mass profile. {\bf Our algorithm works as follows...}

@@

We select a sample of halos in a cubic sub-volumne of $100$ \hMpc on a
side centered on the most massive halo in the simulation at
$z=0$\footnote{This corresponds to the \texttt{miniMDR1} database in
  the MultiDark webpage}. We select first all the halos at $z=0$
detected with a Friends-of-Friends (FoF) algorithm with masses in the
interval $10^{11}\leq M_{\rm FoF}/\hMsun \leq 10^{15}$. The FoF
algorithm ran with a linking length of $0.17$ times the average
interparticle distance. This choice translates into an overdensity
$\Delta_h\sim 700$ that is dependent on the halo concentration
\citep{More2011}.

@@

Finally we compare this results with the values obtaned by BDM, since
the number of halos obtained by FOF and BDM is different, each BDM
halo gets related with the nearest halo in FOF. We compute two
concentrations, one where the overdensity limit is $360\rho_{back}$
(like in BDMV) an other where the overdensity limit is
$740\rho_{back}$ (like in BDMW).

@@

\subsection{Mock Halos}
\begin{figure}[H]
\caption{FIXME: Test results}
\end{figure}

\subsection{Simulation Dat}

@@

\subsection{Implication for comparison against observations}

>>>>

The method we use to generate the halos is based on the integrated
mass profile. Given the number of particles $n$ and the concentration $c$ we define the mass element as $\delta m = 1/n$ (this corresponds to the mass of each particle, such that the total mass is one). Then for each number $k$ from $1$ to $n$ we find the value of $r$ such that
\begin{equation}
m(<r;c)-k \cdot \delta m 
\end{equation}
is zero using Ridders' method. This value of $r$ will be the radius of the $k$th particle of the generated halo, then polar and azimuthal angles $\theta$ and $\phi$ are generated randomly. Finally these three coordinates are transformed into cartesian coordinates $(r,\theta,\phi) \rightarrow (x,y,z)$. This process is repeated $n$ times in order to generate the $x,y,z$ coordinates for each particle.

@@

We select a sample of halos in a cubic sub-volumne of $100$ \hMpc on a
side centered on the most massive halo in the simulation at
$z=0$\footnote{This corresponds to the \texttt{miniMDR1} database in
  the MultiDark webpage}. We select first all the halos at $z=0$
detected with a Friends-of-Friends (FoF) algorithm with masses in the
interval $10^{11}\leq M_{\rm FoF}/\hMsun \leq 10^{15}$. The FoF
algorithm ran with a linking length of $0.17$ times the average
interparticle distance. This choice translates into an overdensity
$\Delta_h\sim 400-700$ that is dependent on the halo concentration
\citep{More2011}.

@@

@@

\subsection{Mock Halos}
\label{sec:results_mocks}
\begin{figure}[H]
\caption{FIXME: Test results}
\end{figure}

\subsection{Simulation Data}
\label{sec:results_mocks}

@@

\subsection{Implication for comparisons against observations}
